\section{Experience}
\vspace{-0.2cm}
\begin{entrylist}
  \entry{2015--now}{Alibaba Cloud Computing (AliCloud)}{Hangzhou, China}{
    \jobtitle{Senior R\&D Engineer}{
      Virtualization Team in Elastic Computing Service (ECS) Group}{
      \job{
        Develop test cases of high-performance virtual switch based on
        \textbf{nosetest} framework. Build CI system with \textbf{Jenkins}
        and \textbf{Gerrit}.}\\
      \job{
        Lead the \textbf{GPU SRIOV} technology integration on AliCloud.
        Develop customizing features including resource management and scheduling
        policy. Develop test cases based on \textbf{libvirt-test}.}\\
      \job{
        \textbf{QEMU/KVM} optimization to timer and interrupt. Implement
        hypervisor \textbf{live-upgrading} with \textbf{VFIO} device
        passthrough.}\\
      \job{
        Evaluate HPC, deep learning bussiness on virtualization environment
        with \textbf{LINPACK}, \textbf{Caffe}, \textbf{Tensorflow} and
        \textbf{Docker}.}\\
      \job{
        \textbf{GRID VGPU} technology integration based on
        vfio-vgpu framework.}}}\\
  \entry{2012--2015}{Advanced Micro Devices (AMD)}{Shanghai, China}{
    \jobtitle{Software Engineer}{
      Linux Base Graphics Driver Team}{
      \job{
        Investigate in SRIOV GPU virtualization. Simulate to verify the
        software design introduced latency of graphics context switch.}\\
      \job{
        Optimize Linux graphics driver for surface capture, reduce the
        buffer migration overhead.}\\
      \job{
        Develop features and fix bugs in \textbf{Catalyst} driver stack including
        \textbf{DRM\slash DRI}, \textbf{DDX\slash GLX}.}\\
      \job{Bring up 2 generations of AMD GPUs \textit{Tonga and Iceland}.}}\\
    \jobtitle{Sr. Software Engineer}{
      GPU Virtualization Group}{
      \job{
        Develop on hybrid Linux graphics KMD driver \textbf{AMDGPU} derived
        from \textbf{RADEON}.}\\
      \job{
        Develop vSGA GPU utilities for \textbf{VMware ESXi}.
        Fix bugs for vSGA hypervisor driver}\\
      \job{
        Develop SR-IOV GPU physical function driver on \textbf{VMware ESXi}
        and \textbf{Xen} platforms}}}
\end{entrylist}
